---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# simpleRank

<!-- badges: start -->
<!-- badges: end -->

simpleRank implements the Mann-Kendall rank correlation coefficient and respective test, as well as a way to calculate the Sen slope (and test for its significance). Other existing packages, as for example, the [trend package by Thorsten Pohlert](https://CRAN.R-project.org/package=trend) don't allow for irregular and/or duplicated ranks while [McLeod's implementation](https://CRAN.R-project.org/package=Kendall) further prohibits one-sided tests for significance.

This is a toy package which was mainly created to get used to writing packages for R. While it (at some point) will be feature-complete in the sense that it's usable, I'm not sure if you'd really want wo use it.

## Installation

Download and install this package from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Florian-Katerndahl/simpleRank")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(simpleRank)
## basic example code
```
